DynaProg for Scala

### 2012-12-02 docs/roadmap/draft.tex
Nits.

\subsection*{Abstract}
Dynamic programming is a common pattern of Computer Science used in various domains. Yet underlying matrix recurrences might be difficult to express and error prone. Additionally, domain experts might not have the skills to make an efficient parallel implementation. In this paper, we leverage the Scala / LMS infrastructure to implement a domain specific language (DSL) for dynamic programming on heterogeneous platforms, which allows to write concise and efficient programs. Our contributions are: \ul
\item {\color{red} Reuse of existing compiler technology for a specific purpose}
%\item Classification of DP problems characteristics (matrix shape, dependency graph, ...)
\item Grammar embedded in Scala (DSL) to express DP problems efficiently
%\item State of the art parallel implementation of these classes on GPUs
%\item Normalization of the grammar into efficient productions
\item Systematic approach to generate and process backtracking information (better than gapc)
\item Code generator to transform a grammar into efficient code for CPU, GPU and FPGA
\ule

>>>>

\subsection*{Abstract}
Dynamic programming is a common pattern of Computer Science used in various domains. Yet underlying matrix recurrences might be difficult to express and error prone. Additionally, domain experts might not have the skills to make an efficient parallel implementation. In this paper, we leverage the Scala / LMS infrastructure to implement a domain specific language (DSL) for dynamic programming on heterogeneous platforms, which allows to write concise and efficient programs. Our contributions are: \ul
\item Reuse of existing compiler technology (fusion) for a specific purpose
%\item Classification of DP problems characteristics (matrix shape, dependency graph, ...)
\item Grammar embedded in Scala (DSL) to express DP problems concisely
%\item State of the art parallel implementation of these classes on GPUs
%\item Normalization of the grammar into efficient productions
\item Systematic approach to generate and process data (top-down/bottom-up) and backtracking information (focus on running time and memory efficiency)
\item Code generator to transform a grammar into efficient code for CPU, GPU (and FPGA)
\ule
